Commutative Character Sheaves

### 2015-09-18 followup.tex
Descent re-written

\section{Descent to the abelianization}

@@

\begin{proof}
By construction, $c : G \times G \to G\der$ is dominant. 
Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_{G\der})
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}.
\end{align*}
Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$.
\todo{Produce or find a proof.} It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
\end{proof}

Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.

@@

\begin{proof}
It follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. To see this, we observe that
every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$, as follows.
Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
Then $n = m \circ (j \times \id)$, so
\begin{align*}
n^* \cs{L} 
&= (m \circ (j \times \id))^* \cs{L}\\
&= (j \times \id))^* m^*\cs{L}\\
&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
&= (j^*\cs{L}) \boxtimes \cs{L}\\
&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
&= (\EE)_C \boxtimes \cs{L}\\
&= p^* \cs{L}.
\end{align*}
Thus, $\cs{L}$ is $G\der$-equivariant.
\end{proof}

The quotient $q : G \to G\ab$ with kernel $G\der$  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{n}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]

\begin{lemma}\label{lem:smooth_coeq}
The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor.
\end{lemma}

[I don't have a proof of this yet.]\todo{Either true or it becomes a condition on $G$.}

\[
\begin{tikzcd}
\CCS(G\der \times G)
& \arrow{l}[shift left,swap]{n^*}
  \arrow{l}[shift right]{p^*}
\CCS(G) 
&&\arrow{ll}[swap]{q^*} 
\CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\
& & \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
\end{tikzcd}
\]

\begin{theorem}\label{thm:descent}
 Let $G$ be a smooth group scheme over $\Fq$ 
 and let $q : G \to G\ab$ be its abelianization. 
 Then  
\[
q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
\]
is an equivalence of rigid monoidal categories.
\end{theorem}

\begin{proof}
It follows from Lemma~\ref{lem:smooth_coeq} that $q$ is an 
effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack? That might require a small section, just before this one.}
See appendix for details.
%
Combining this with Proposition~\ref{prop:Gder-equivariance}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
\end{proof}

\begin{remark}
A great tragedy of nomenclature: an equivariant sheaf is not a sheaf that is equivariant. \todo{I will explain this.\\ -CC} 
\end{remark}

 \begin{corollary}
 Trace of Frobenius induces an isomorphism
 \[
 \CCSiso{G} \to G(\Fq)^*.
 \]
 \end{corollary}

 \begin{proof}
 By descent along $G \to G/C$, pullback induces an equivalence of categories between $C$-equivariant local systems on $G$ local systems on  $G/C$. \todo{I need to explain what's going on here. See appendix.\\ -CC}
  The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
 $G(\Fq)/C(\Fq)$, which equals $(G/C)(\Fq)$ since $C$ is simply connected.
 \end{proof}

@@

 Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the rank-$1$ character sheaf corresponding
 to the cover
 \[
 1 \to \mu_n \to \SL_n \to \PGL_n \to 1
 \]
 is not commutative.  Explain how our character sheaves are not just representations of a fundamental group
 (or are they?), but instead have extra data like $\mu$ and $\phi$.
\todo{I got this wrong. I think our sheaves are not extra information in the commutative case. Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case. So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper. \\ -CC}

\section{Application to certain supercuspidal representations of $p$-adic groups}

[A basic question which I think we must answer but which we can maybe skate around for now:
When is the Suzuki transform of a K-variety representable as a k-scheme?

@@

@@

Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$. Moreover, $C_0$ admits a smooth integral model $\underline{C}$ \todo{Under construction. \\ -CC}

\appendix

\section{Descent along smooth fibrations}

Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$.

A principal $G$-bundle $f : X\to Y$ is a coequalizer of $m$ and projection $G\times X \to X$  
which is locally trivial in the following sense.
First, there is an open covering $\{ V_n\}$ of $Y$ such that, for each $V$ in this covering, the lower coequalizer diagram is a base change of the one above
\[
\begin{tikzcd}
G\times X
 \arrow{rr}[shift left]{m}
  \arrow{rr}[shift right,swap]{\text{proj'n}}
&& X \arrow{r}{f} &  Y\\
G\times  (G\times V) \arrow{u}
 \arrow{rr}[shift left]{\text{mult'n in $G$}}
  \arrow{rr}[shift right,swap]{\text{proj'n}}
&& G\times V \arrow{u}  \arrow{r} &  \arrow{u} V;
\end{tikzcd}
\]

and the following diagram commutes
\[
\begin{tikzcd}
G\times  f^{-1}(V)
 \arrow{r}[shift left]{m}
  \arrow{dr} 
& f^{-1}(V) \arrow{r} \arrow{d}{t_V} &  V \\
& G\times V \arrow{ur} & 
\end{tikzcd}
\]

and isomorphisms ${t}_n : f^{-1}{V}_n \to {G}\times {V}_n$ such that  ${f}$ is given locally by ${f}_n = p \circ {t}_n$ (so ${f}_n : {f}^{-1}{Y}_n \to {Y}_n$) and the action ${m}_{X}$ of ${G}$ on ${X}$ is given locally by ${t}_n \circ {m}_n =  ({m} \times \id) \circ (\id\times{t}_n)$ (so ${m}_n : {G}\times{f}^{-1}{Y}_n \to {f}^{-1}{Y}_n$).

Let $\Loc^1(X)$ be the category of rank-$1$ local systems on $X$ and let $\Loc_G^1(X)$ be the category of $G$-equivariant rank-$1$ local systems on $X$.

\begin{proposition}
Let $G$, $X$ and $Y$ be smooth.
Let $f : X \to Y$ be a $G$-torsor.
Then the comparison functor, pictured below,
\[
\begin{tikzcd}
%\Loc^1(G \times X)
%& \arrow{l}[shift left,swap]{m^*}
%  \arrow{l}[shift right]{p^*}
\Loc^1(X) 
&&\arrow{ll}[swap]{f^*} 
\Loc^1(Y) \arrow{dl}{\text{comparison}}\\
& \arrow{ul}{\text{forget}} \Loc^1_G(X) & 
\end{tikzcd}
\]
is an equivalence.
\end{proposition}

\begin{proof}
This is well-known. We include a proof only for completeness.

To simplify notation slightly, set ${X}_n \ceq {f}^{-1}{Y}_n$; also, let ${j}_n : {Y}_n \to {Y}$ and ${i}_n : {X}_n \to {X}$ denote inclusions.

Then $f : X \to Y$ is a smooth, regular epimorphism with kernel pair $m, p: G\times X\to X$, and t

Consider the following commuting diagram:
\[
\begin{tikzcd}
H\times X \arrow{d}{\id\times f} \arrow{r}{m_X}&\to X\arrow{d}{f}\\
H\times Y \arrow{r}{m_Y} &\to Y\\
H\times X \arrow{r}{p_2} \arrow{u}{\id\times f} &\to X \arrow{u}{f}
\end{tikzcd}
\]
Thus,
\[
\begin{aligned}
m_X^*[\dim H] f^*[d] A
&\iso (f\circ m_X)^* [d+\dim H]A  &\\
&\iso (m_Y\circ (\id\times f))^*[d+\dim H]A & \text{$f$ is equivariant}\\
&\iso (\id\times f)^*[d] m_Y^*[\dim H] A &\\
&\iso  (\id\times f)^*[d] p_2^*[\dim H] A &\text{$A$ is $H$-equivariant}\\
&\iso  (p_2\circ (\id\times f))^*[d+\dim H] A &\\
&\iso (f\circ p_2)^*[d+\dim H]A & \\
&\iso p_2^*[\dim H] f^*[d]A. &
\end{aligned}
\]
This completes the proof that $f^*[d]A$ is an $H$-equivariant perverse sheaf on $X$.

Let $\mathcal{F} = {f}^*[\dim{P}] \mathcal{G}$.

To show that $\mathcal{F}$ is equivariant we must find an isomorphism $\mu : {m}^* \mathcal{F} \to p^* \mathcal{F}$ in $D^b_c({P}\times{X}, \EE)$ such that ${e}^*\mu = \id_{\mathcal{F}}$, where ${e} : {X} \to {P}\times{X}$ is the section defined by $x \mapsto (1,x)$. To see this, consider the restriction of ${m}^* \mathcal{F}$ to ${P}\times{X}_n$:
\begin{eqnarray*}
({m}^* \mathcal{F})\vert_{{P}\times {X}_n}
	&=& (\id\times {i}_n)^* {m}^* {f}^* \mathcal{G} [\dim{P}]\\
	&\iso& ({f}\circ {m} \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
	&=& ({f} \circ {i}_n \circ {m}_n)^* \mathcal{G} [\dim{P}].
\end{eqnarray*}
On the other hand, the restriction of $p^* \mathcal{F}$ to ${P}\times{X}_n$ is 
\begin{eqnarray*}
(p^* \mathcal{F})\vert_{{P}\times {X}_n}
	&=& (\id\times {i}_n)^* p^* {f}^* \mathcal{G} [\dim{P}]\\
	&\iso& ({f}\circ p \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
	&=& ({f} \circ {i}_n \circ p)^* \mathcal{G} [\dim{P}].
\end{eqnarray*}
Since ${f} \circ {i}_n \circ {m}_n = {f} \circ {i}_n \circ p$, we have $({m}^* {\mathcal{F}})\vert_{{P}\times {X}_n} \iso (p^* \mathcal{F})\vert_{{P}\times {X}_n}$. Since $\cup_n {P}\times{X}_n$ is an open cover for ${P}\times{X}$, this gives the isomorphism we seek.

Next, suppose $\mathcal{F} \in \obj{\mathcal M}{X}$ is equivariant; thus, $\mathcal{F} \in \obj{\mathcal M}_{P}{X}$. Let $\mathcal{F}_n$ denote the restriction of $\mathcal{F}$ to ${X}_n$.

Recall that ${m}: {P}\times{X} \to {X}$ is given locally by ${m}_n : {P}\times {X}_n \to {X}_n$, as above. Restricting the isomorphism $\mu_{\mathcal{F}} : {m}^* \mathcal{F} \to p^* \mathcal{F}$ to ${P}\times{X}_n$ yields the isomorphism $\mu_{\mathcal{F}_n} : {m}_n^* \mathcal{F}_n \to p^* \mathcal{F}_n$. Thus, $\mathcal{F}_n$ is an equivariant perverse sheaf. Now, let ${e}_n : {Y}_n \to {X}_n$ be the section of ${f}_n : {X}_n \to {Y}_n$ corresponding to $1\in {P}(\Fq)$ (so ${e}_n$ is the unique morphism of varieties such that $({t}_n \circ {e}_n) (y) = (1,y)$). Define
\begin{equation}\label{equation: torsor 5}
	\mathcal{F}'_n \ceq {e}_n^* \mathcal{F}_n [-\dim{P}].
\end{equation}
Then $\mathcal{F}'_n \in \obj D^b_c({Y}_n, \EE)$. By standard glueing arguments, the collection of $\mathcal{F}'_n \in\obj D^b_c({Y}_n, \EE)$, as ${Y}_n$ ranges over the open cover of ${Y}$ fixed above, uniquely determines an object $\mathcal{G}$ of $D^b_c({Y}, \EE)$.

It remains to be shown that $\mathcal{G}$ is a perverse sheaf. Again, we work locally. For each such $n$,
\begin{eqnarray*}
{f}_n^*[\dim{P}] \mathcal{F}'_n 
	&=& {f}_n^*[\dim{P}] {e}_n^* \mathcal{F}_n [-\dim{P}]\\
	&\iso& ({e}_n\circ {f}_n)^* \mathcal{F}_n.
\end{eqnarray*}
Let ${u}_n : {X}_n \to {P}\times{X}_n$ be the section of ${m}_n : {P}\times{X}_n \to {X}_n$ corresponding to $1$ (so ${u}_n$ is the unique morphism of varieties such that $(\id\times{t}_n)\circ {u}_n \circ {t}_n^{-1} (h,y) = (h,1,y)$). The domain of ${u}_n^*\mu_{\mathcal{F}_n}$ is ${u}_n^*{m}_n^* \mathcal{F}_n \iso ({m}_n \circ {u}_n)^* \mathcal{F}_n = \mathcal{F}_n$, since ${u}_n$ is a section of ${m}_n$; the codomain of ${u}_n^* \mu_{\mathcal{F}_n}$ is ${u}_n^* p^* \mathcal{F}_n \iso (p\circ {u}_n)^*\mathcal{F}_n$. Since $p\circ {u}_n = {e}_n \circ {f}_n$, it follows that 
\[
{u}_n^* \mu_{\mathcal{F}_n} : \mathcal{F}_n \to {f}_n^*[\dim{P}] \mathcal{F}'_n
\]
is an isomorphism in $D^b_c({X}_n, \EE)$. By \cite[Prop~4.2.5]{BBD} and the fact that ${\mathcal M}{X}_n$ is stable in $D^b_c({X}_n, \EE)$ under isomorphisms, it follows that $\mathcal{F}'_n \in \obj {\mathcal M}{Y}_n$. By standard glueing arguments, the collection of isomorphisms ${u}_n^* \mu_{\mathcal{F}_n} \in \mor{\mathcal M}{X}_n$, as ${X}_n$ ranges over the open cover of ${X}$ fixed above, uniquely determines an isomorphism in \[
\Hom_{D^b_c({X}, \EE)}(\mathcal{F},{f}^*[\dim{P}] \mathcal{G}).
\]  
From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{proposition: torsor}.
\end{proof}

\begin{proposition}\label{proposition: more torsor}
Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected. Then ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is an equivalence of categories and ${\mathcal M}_{P}{X}$ is a thick subcategory of ${\mathcal M}{X}$.
\end{proposition}

\begin{proof}
By \cite[Prop~4.2.5]{BBD} we know that ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}{X}$ is full and faithful. Let $\mathcal{G}$ be a perverse sheaf on ${Y}$. From the proof of Proposition~\ref{proposition: torsor} we have seen that $\mathcal{F} \ceq {f}^*[\dim{P}] \mathcal{G}$ is an equivariant perverse sheaf on ${X}$ and that ${f}^*[\dim{P}] \phi$ is an equivariant morphism in ${\mathcal M}{X}$ for each morphism $\phi$ in ${\mathcal M}{Y}$. Thus, ${f}^*[\dim{P}]$ is a functor from ${\mathcal M}{Y}$ to ${\mathcal M}_{P}{X}$. Thus, ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is full and faithful. Proposition~\ref{proposition: torsor} tells us that this functor is essentially surjective. Thus, ${f}^*[\dim{P}]$ is an equivalence. The last clause of Proposition~\ref{proposition: more torsor} follows from \cite[4.2.6]{BBD}.
\end{proof}

\begin{definition}\label{definition: descent}
Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected. Let ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ denote the adjoint of the equivalence ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ (see Proposition~\ref{proposition: more torsor}). In particular, ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ is an equivalence of categories.
\end{definition}

\begin{corollary}
Suppose $H$ is a connected group acting smoothly on $X$.
If $A\in {\mathcal M} X$ is $H$-equivariant and $B\in {\mathcal M} X$ is a subquotient of $A$, then $B$ is also $H$-equivariant.
\end{corollary}

\begin{proof}
(Following \cite[(1.9.1)]{CS}.)
Let the action of $H$ on $Y$ is given by $m : H\times X \to X$. This is a smooth morphism with connected fibres, by hypothesis. Thus, $m^*[\dim H]$ is an equivalence of categories, by Proposition~\ref{proposition: more torsor}.  Since equivalences take epimorphisms to epimorphisms and monomorphisms to monomorphisms, it follows that $m^*[\dim H]B$ is a subquotient of $m^*[\dim H]A$. Since $A$ is an $H$-equivarient perverse sheaf on $X$, we have $m^*[\dim H]A \iso p_2^*[\dim H]A$. On the other hand, $p_2 : H\times X \to X$ is also a smooth morphism with connected fibres of dimension $H$, so by Proposition~\ref{proposition: more torsor}, $p_2^*[\dim H]$ identifies ${\mathcal M}_H X$ with a thick subcategory of ${\mathcal M} (H\times X)$. Since $m^*[\dim H]B$ is a subquotient of $p_2^*[\dim H]A$, it follows that there is some $C\in {\mathcal M} X$ such that $p_2^*C \iso m^*[\dim H]B$ restricting this isomorphism from $H\times X$ to $\{ e\} \times X$ (on which $m$ and $p_2$ agree), yields $C\iso B$. Thus, $p_2^*B \iso m^*[\dim H]B$, from which is follows that $B$ is $H$-equivariant.
\end{proof}

>>>>

\section{Descent for commutative character sheaves}

\subsection{Quotients}

Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.

Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; let $p : H\times_S G \to G$ be projection.

\subsection{$H$-equivariance}

An $H$-equivariant rank-$1$ character sheaf on $H$ is a rank-$1$ character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar m}_H^*\gcs{L} \to {\bar p}_H^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
\begin{enumerate}
\item
\[
\begin{tikzcd}
\ &  m_0^*  m^*\, \mathcal{L} \arrow{r}{m_0^*\nu} & m_0^* p^*\, \mathcal{L} & \\
m_1^* m^*\, \mathcal{L} \arrow{dr}[swap]{m_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* m^*\, \mathcal{L} \\
& m_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
\end{tikzcd}
\]
where $m_0(a,b,x) = (a,m(b,x))$ and $m_1(a,b,x) = (m(ab),x)$ and $p_2(a,b,x) = (b,x)$;
\item
\end{enumerate}
Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
\subsection{Descent}

We now suppose that $H$ is normal in $G$, that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.

In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
\[
\begin{tikzcd}
\CCS(G) &&\arrow{ll}[swap]{q^*} 
\CCS(G') \arrow{dl}{\text{`comparison'}}\\
& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
\end{tikzcd}
\]

\begin{lemma}\label{lem:descent}
If the quotient $q : G \to G'$ is a $G$-torsor in the etale topology, then the comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
\end{lemma}

\begin{proof}
By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. 
\end{proof}

\subsection{Dominant morphisms and local systems}

\begin{lemma}\label{lem:dominant}
Suppose $f: X \to Y$ is dominant.
If $\cs{L}\in \Loc(Y)$ and $f^*\cs{L} \iso (\EE)_X$ then $\cs{L} \iso (\EE)_Y$.
\end{lemma}

\begin{proof}
The group homomorphism $\pi_1(f): \pi_1(X, {\bar x}) \to \pi_1(Y, {\bar y})$ is surjective, for all geometric points with $f({\bar x}) = {\bar y}$ ... 
%\todo{Under construction}
\end{proof}

\subsection{Derived subgroup}

@@

\begin{proof}
By construction, $c : G \times G \to G\der$ is dominant. 
Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_{G\der})
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}.
\end{align*}
Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
\end{proof}

@@

\begin{proof}
%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
Then $n = m \circ (j \times \id)$, so
\begin{align*}
n^* \cs{L} 
&= (m \circ (j \times \id))^* \cs{L}\\
&= (j \times \id))^* m^*\cs{L}\\
&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
&= (j^*\cs{L}) \boxtimes \cs{L}\\
&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
&= (\EE)_C \boxtimes \cs{L}\\
&= p^* \cs{L}.
\end{align*}
Thus, every commutative character sheaf $\cs{L}$ on $G$ is $G\der$-equivariant.
It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
\end{proof}

\subsection{Abelianization}

By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
This exists in schemes since  . . . 
%\todo{Proof needed}
%  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{n}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]

\begin{proposition}\label{prop:Gab-descent}
Let $G$ be a smooth group scheme over $\Fq$ 
 and let $q : G \to G\ab$ be its abelianization. 
 Then  
\[
\CCS(G\ab) \longrightarrow \CCS_{G\der}(G)
\]
is an equivalence of categories.
\end{proposition}

\begin{proof}
The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.} so the result follows from Lemma~\ref{lem:descent}.
\end{proof}

\begin{theorem}\label{thm:Gab-descent}
 Let $G$ be a smooth group scheme over $\Fq$ 
 and let $q : G \to G\ab$ be its abelianization. 
 Then  
\[
q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
\]
is an equivalence of rigid monoidal categories.
\end{theorem}
\begin{proof}
Combine Propositions~\ref{prop:Gder-equivariance} and \ref{prop:Gab-descent}.
\end{proof}

 \begin{corollary}
The following is a commuting diagram of isomorphisms:
\[
\begin{tikzcd}
\CCSiso{G} \arrow{r} & G(\Fq)^*\\
\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* . \\
\end{tikzcd}
\]
 \end{corollary}

 \begin{proof}
 By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
Since $G\der$ is simply connected,\todo{Proof needed}, $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
Thus, all characters of $G(\Fq)$ factor through
 $G\ab(\Fq)$. . . . 
 The isomorphisms are compatible because  . . . 
 \end{proof}

@@

 Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the rank-$1$ character sheaf corresponding
 to the cover
 \[
 1 \to \mu_n \to \SL_n \to \PGL_n \to 1
 \]
 is not commutative.  
 %Explain how our character sheaves are not just representations of a fundamental group (or are they?), but instead have extra data like $\mu$ and $\phi$.
%\todo{I got this wrong. I think our sheaves are not extra information in the commutative case. Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case. So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper. \\ -CC}

\section{Applications to supercuspidal representations}

\subsection{Commutative quasicharacter sheaves}

@@

 \subsection{Geometric types for supercuspidal representations}

@@

Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$. Moreover, $C_0$ admits a smooth integral model $\underline{C}$ ...

\subsection{Toral supercuspidal representations of $p$-adic groups}
